---
title: "day 18 - ggplot2"
author: "Enlik Tjioe"
date: "1/18/2021"
output: html_document
---


## References
- https://www.dataquest.io/blog/data-visualization-in-r-with-ggplot2-a-beginner-tutorial/
- http://zevross.com/blog/2014/08/04/beautiful-plotting-in-r-a-ggplot2-cheatsheet-3/

## Import Data
```{r}
library(tidyverse)
life_expec <- read.csv("data/life_expec.csv")
life_expec
```
```{r}
colnames(life_expec)
```

```{r}
life_expec %>% 
  filter(Year == 2000)
```


### Blank Graph Beginner Mistake in ggplot2
```{r}
life_expec <- life_expec %>%
  filter(Race == "All Races", Sex == "Both Sexes")

life_expec %>%
  ggplot()
```

### Get the axes using ggplot Grammar of Graphics
```{r}
life_expec %>%
  ggplot(aes(x = Year, y = Average.Life.Expectancy..Years.))
```

### Specifying Geoms
```{r}
life_expec %>%
  ggplot(aes(x = Year, y = Average.Life.Expectancy..Years.)) +
  geom_line()
```

### Adding a Title and Axis Labels
```{r}
life_expec %>% # data layer
  ggplot(aes(x = Year, y = Average.Life.Expectancy..Years.)) + # axes layer
  geom_line() + # geom layer
  labs(  # annotations layer
    title = "United States Life Expectancy: 100 Years of Change",
    y = "Average Life Expectancy (Years)"
  )
```

## From ZevRoss Tutorial
```{r}
nmmaps<-read.csv("data/chicago-nmmaps.csv", as.is=T)
nmmaps$date<-as.Date(nmmaps$date)
nmmaps<-nmmaps[nmmaps$date>as.Date("1996-12-31"),]
nmmaps$year<-substring(nmmaps$date,1,4)
head(nmmaps)
```
```{r}
g<-ggplot(nmmaps, aes(date, temp))+geom_point(color="firebrick")
g
```
```{r}
g<-g+ggtitle('Temperature')
g
```

```{r}
g+theme(plot.title = element_text(size=20, face="bold", 
    margin = margin(10, 0, 10, 0)))
```
### Additional Font Library
```{r}
library(extrafont)
g+theme(plot.title = element_text(size=30,lineheight=.8, 
  vjust=1,family="Bauhaus 93"))
```
```{r}
g<-g+ggtitle("This is a longer\ntitle than expected")
g+theme(plot.title = element_text(size=20, face="bold", vjust=1, lineheight=0.6))
```
### Working with Legends
```{r}
g<-ggplot(nmmaps, aes(date, temp, color=factor(season)))+geom_point()
g
```
### Turn off the Legend Title
```{r}
g+theme(legend.title=element_blank())
```

### Change the style of Legend Title
```{r}
g+theme(legend.title = element_text(colour="chocolate", size=16, face="bold"))
```
### Change the Title of Legend
```{r}
g+theme(legend.title = element_text(colour="chocolate", size=16, face="bold"))+
  scale_color_discrete(name="This color is\ncalled chocolate!?")
```
### Change the background box in legend
```{r}
g+theme(legend.key=element_rect(fill='pink'))
```
### Change the size of symbol in the legend only
```{r}
g+guides(colour = guide_legend(override.aes = list(size=6)))
```

### Leave the Layer off the Legend
```{r}
g+geom_text(data=nmmaps, aes(date, temp, label=round(temp)), size=4)
```
## Convert ggplot2 plot to Plotly

- http://zevross.com/blog/2014/09/10/quickly-create-online-and-interactive-plots-using-plot-ly/
- https://plotly.com/ggplot2/getting-started/

### Dependencies
```{r}
#install.packages("devtools")
#library("devtools")
#install_github("ropensci/plotly")
```


```{r}
g <- ggplot(nmmaps, aes(date, temp, color=factor(season)))+  geom_point() +   
  scale_color_manual(values=c("dodgerblue4", "darkolivegreen4",  
                              "darkorchid3", "goldenrod1"))
g
```

```{r}
library(plotly)
g_plotly <- ggplotly(g)
g_plotly
```

